### 2013-07-23 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding to nonlinear analysis

For each of the benchmark problems, we will present the results of
computations using FANM and directly compare them to results using a
Newton-Krylov method in order to verify the correctness of FANM and
its applicability to fluid problems. For each case, we will compare
the global minimum, maximum, and average values for fluid velocity,
pressure, and temperature where applicable. If the values for these
quantities computed using FANM match those computed using a production
Newton-Krylov method, the implementation will be deemed correct for
the purposes of this work. In addition, we will report the tolerance
to which the nonlinear residual was converged as an additional means
of comparison for correctness.

Given the difficulty of these benchmark problems, the linear solve at
each Newton step was preconditioned with an algebraic multigrid
method, a common technique for preconditioning these equations
\citep{ghia_high-re_1982,evans_enhanced_2007}. Without multigrid
preconditioning, the residual in MCSA was observed to
stagnate. Typically this happens because the Richardson iteration will
damp the higher order error modes on the scale of the computational
grid used to solve the problem but will miss lower order error
modes. In terms of Monte Carlo, this stagnation manifests itself in
histories that simply do no terminate and therefore no solution is
acquired.

For FANM, this preconditioning was required to reduce the spectral
radius of the Jacobian operators generated at each Newton step and for
the Newton-Krylov solutions this preconditioning was required to
obtain good convergence properties although it was not necessary for
convergence. For every benchmark calculation, both FANM and
Newton-Krylov were preconditioned with the same multigrid parameters
such that the conditioning of the system would not be a factor in the
verification of the method or the performance comparison in the
following section. In addition, the same nonlinear solver parameters
including globalization and forcing term strategies were used with
both methods. As with the radiation transport calculations in the
previous chapter, algrebraic preconditioning with the multigrid method
results in dense linear systems. To mitigate this, the reduced domain
approximation was again applied to the Monte Carlo solution within the
MCSA solve occuring at each nonlinear iteration. The values used for
the approximation will be given for each benchmark problem.

@@

A Drekar model of thermal convection cavity problem was solved using
both the Newton-Krylov solver and a FANM solver for Rayleigh numbers
of \sn{1}{3}, \sn{1}{4}, \sn{1}{5} and \sn{1}{6} on a $50 \times 50$
square grid. Table~\ref{tab:thermal_convection_parameters} gives the
physical parameters of the problem and
Table~\ref{tab:convection_mcsa_parameters} gives the MCSA solver
parameters used within the FANM method. Variation in the Rayleigh
number of the system was achieved by keeping the parameters given in
Table~\ref{tab:thermal_convection_parameters} constant and varying
temperature of the hot side of the cavity. In addition to multigrid
preconditioning for the linear solution at each Newton step,
backtracking as outlined in Shadid's work \citep{shadid_inexact_1997}
was used as a means of globalization to assist the Newton correction
computation while the forcing term was computed at each Newton step
using method 2 from Shadid's work. In this forcing term method,
nonlinear residuals from the two previous Newton steps are used to
inform the choice of the forcing term for the next step.

@@

For the verification calculations, at each Rayleigh number variation
the global minimum, maximum, and average values were recorded for
fluid velocity in the x and y directions, fluid pressure, and fluid
temperature. Tables~\ref{tab:convection_ra1e3_results},
\ref{tab:convection_ra1e4_results},
\ref{tab:convection_ra1e5_results}, and
\ref{tab:convection_ra1e6_results} give the results of these
computations. It should be noted that the negative pressures computed
are due to a relative pressure being reported. For each of the data
points presented, both Newton-Krylov solutions and FANM solutions
computed identical numerical results for all of these global
values. No variation in solution was noted for each of the
computations larger than the tolerance of the converged nonlinear
residual norms given in
Table~\ref{tab:convection_residual_norm_comparison}. Variations in the
convergence behavior and differences in performance for these
solutions will be analyzed in the following section.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      \sn{1}{3} & \sn{4.542}{-14} & \sn{1.208}{-14} \\
      \sn{1}{4} & \sn{1.045}{-12} & \sn{7.012}{-13} \\
      \sn{1}{5} & \sn{1.784}{-12} & \sn{1.059}{-12} \\
      \sn{1}{6} & \sn{3.404}{-12} & \sn{3.479}{-12} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:convection_residual_norm_comparison}
\end{table}

@@

A Drekar model of thermal convection cavity problem was solved using
both the Newton-Krylov solver and a FANM solver for Reynolds numbers
of 100, 300, 500, and 700 on a $50 \times 50$ square
grid. Table~\ref{tab:lid_driven_parameters} gives the physical
parameters of the problem and
Table~\ref{tab:driven_mcsa_parameters} gives the MCSA solver
parameters used within the FANM method. Variation in the Reynolds
number of the system was achieved by keeping the parameters given in
Table~\ref{tab:lid_driven_parameters} fixed and varying the
fluid velocity in the $x$ direction on the top boundary. In addition
to multigrid preconditioning for the linear solution at each Newton
step, a polynomial line search method was used as a means of
globalization assisting the Newton correction computation as outlined
by Pawlowski in \citep{pawlowski_globalization_2006} while the forcing
term was again computed using method 2 from Shadid's work
\citep{shadid_inexact_1997}.

@@

For the verification calculations, at each Reynolds number variation
the global minimum, maximum, and average values were recorded for the
fluid velocity in the x and y directions and the fluid
pressure. Tables~\ref{tab:driven_re100_results},
\ref{tab:driven_re300_results}, \ref{tab:driven_re500_results}, and
\ref{tab:driven_re700_results} give the results of these
computations. As with the thermal convection problem, the negative
pressures computed are due to a relative pressure being reported. For
each of the data points given, both Newton-Krylov solutions and FANM
solutions computed identical numerical results for all of these global
values. The norm of the converged nonlinear residual for the
calculations is given in
Table~\ref{tab:driven_residual_norm_comparison}. All computed global
values were within these tolerances.

@@

A Drekar model of the backward facing step problem was solved using
both the Newton-Krylov solver and a FANM solver for Reynolds numbers
of 200, 300, 400, and 500 on a $20 \times 250$ rectangular
grid. Table~\ref{tab:backward_step_parameters} gives the physical
parameters of the problem and Table~\ref{tab:step_mcsa_parameters}
gives the MCSA solver parameters used within the FANM
method. Variation in the Reynolds number of the system was achieved by
keeping the parameters given in
Table~\ref{tab:backward_step_parameters} fixed and varying the maximum
fluid velocity in the parabolic inlet condition. In addition to
multigrid preconditioning for the linear solution at each Newton step,
a polynomial line search method was used as a means of globalization
assisting the Newton correction computation as outlined by Pawlowski
in \citep{pawlowski_globalization_2006} while the forcing term was
again computed using method 2 from Shadid's work
\citep{shadid_inexact_1997}.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point Iteration & Richardson \\
      Estimator & Adjoint Collision \\
      Histories, Re=200 & 500,000 per iteration \\
      Histories, Re=300 & 500,000 per iteration \\
      Histories, Re=400 & 500,000 per iteration \\
      Histories, Re=500 & 1,000,000 per iteration \\
      Reduced Domain Fill Level, Re=200 & 200 \\
      Reduced Domain Fill Level, Re=400 & 200 \\
      Reduced Domain Fill Level, Re=600 & 200 \\
      Reduced Domain Fill Level, Re=800 & 300 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification MCSA solver
      parameters.} \textit{No relaxation parameters or variance
      reduction techniques were used with MCSA other than the reduced
      domain approximation. Different values of fill level for the
      reduced domain approximation and histories per iteration were
      used at different Reynolds numbers due to convergence
      requirements.}}
  \label{tab:step_mcsa_parameters}
\end{table}

@@

For the verification calculations, at each Reynolds number variation
the global minimum, maximum, and average values were recorded for the
fluid velocity in the x and y directions and the fluid
pressure. Tables~\ref{tab:step_re200_results},
\ref{tab:step_re300_results}, \ref{tab:step_re400_results}, and
\ref{tab:step_re500_results} give the results of these
computations. As with the thermal convection problem, the negative
pressures computed are due to a relative pressure being reported. For
each of the data points given, both Newton-Krylov solutions and FANM
solutions computed identical numerical results for all of these global
values. The norm of the converged nonlinear residual for the
calculations is given in
Table~\ref{tab:step_residual_norm_comparison}. All computed global
values were within these tolerances.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\ 
      Minimum $P$ & \\ 
      Maximum $P$ & \\ 
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 200.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re200_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 300.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 400.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re400_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & \\
      Minimum $U$ & \\
      Maximum $U$ & \\
      \hline
      Average $V$ & \\
      Minimum $V$ & \\
      Maximum $V$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 500.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re500_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      200 & \\
      300 & \\
      400 & \\
      500 & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:step_residual_norm_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      \sn{1}{3} & 5 & 5 \\
      \sn{1}{4} & 7 & 7 \\
      \sn{1}{5} & 9 & 10 \\
      \sn{1}{6} & 11 & 11 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:convection_nonlinear_iter_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{GMRES Iterations}&
      \multicolumn{1}{c}{MCSA Iterations}\\
      \hline
      \sn{1}{3} & 23 & 18 \\
      \sn{1}{4} & 23 & 17 \\
      \sn{1}{5} & 25 & 20 \\
      \sn{1}{6} & 39 & 25 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity total sum of linear
      iterations for all nonlinear iterations.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:convection_linear_iter_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      \sn{1}{3} & 338 \\
      \sn{1}{4} & 336 \\
      \sn{1}{5} & 346 \\
      \sn{1}{6} & 465 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:convection_speedup_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      100 & 6 & 6 \\
      300 & 9 & 9 \\
      500 & 11 & 11 \\
      700 & 14 & 10 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:driven_nonlinear_iter_comparison}
\end{table}

>>>>

For each of the benchmark problems, we will present the results of
computations using FANM and directly compare them to results using a
Newton-Krylov method in order to verify the correctness of FANM and
its applicability to fluid problems. For each case, we will compare
the global minimum, maximum, and average values for fluid velocity and
pressure for all benchmarks and additionally temperature for the
thermal convection cavity problem. If the values for these quantities
computed using FANM match those computed using a production
Newton-Krylov method, the implementation will be deemed correct and
the method deemed valid for the purposes of this work. In addition, we
will report the tolerance to which the nonlinear residual was
converged as an additional means of comparison for correctness.

Given the difficulty of these benchmark problems, the linear solve at
each Newton step was preconditioned with an algebraic multigrid
method\footnote{The ML algebraic multigrid library in the Trilinos
  scientific computing libraries \citep{heroux_overview_2005} was used
  for all problems.}, a common technique for preconditioning these
equations \citep{ghia_high-re_1982,evans_enhanced_2007}. Without
multigrid preconditioning, the residual in MCSA was observed to
stagnate. Typically this happens because the Richardson iteration and
Neumann series on which the Monte Carlo method is based will quickly
damp the higher order error modes on the scale of the computational
grid used to solve the problem but will reduce lower order error modes
at a considerably lower rate. In terms of Monte Carlo, this stagnation
manifests itself in histories that simply do no terminate and
therefore no solution is acquired.

For every benchmark calculation, both FANM and Newton-Krylov were
preconditioned with the same multigrid parameters such that the
conditioning of the system would not be a factor in the verification
of the method or the performance comparison in the following
section. With FANM, this preconditioning was required to reduce the
spectral radius of the Jacobian operators generated at each Newton
step. This preconditioning was required to obtain good convergence
properties for the Newton-Krylov solutions although it was not
necessary for their convergence. In addition, the same nonlinear
solver parameters including globalization and forcing term strategies
were used with both methods. As with the radiation transport
calculations in the previous chapter, algrebraic preconditioning with
the multigrid method results in dense linear systems. To mitigate
this, the reduced domain approximation was again applied to the Monte
Carlo solution within the MCSA solve occuring at each nonlinear
iteration. The values used for the approximation will be given for
each benchmark problem.

@@

A Drekar model of thermal convection cavity problem was solved using
both the Newton-Krylov solver and the FANM solver for Rayleigh numbers
of \sn{1}{3}, \sn{1}{4}, \sn{1}{5} and \sn{1}{6} on a $50 \times 50$
square grid. Table~\ref{tab:thermal_convection_parameters} gives the
physical parameters of the problem and
Table~\ref{tab:convection_mcsa_parameters} gives the MCSA solver
parameters used within the FANM method. Variation in the Rayleigh
number of the system was achieved by keeping the parameters given in
Table~\ref{tab:thermal_convection_parameters} constant and varying
temperature of the hot side of the cavity. In addition to multigrid
preconditioning for the linear solution at each Newton step,
backtracking as outlined in Shadid's work \citep{shadid_inexact_1997}
was used as a means of globalization to assist the Newton correction
computation while the forcing term at all Rayleigh numbers but
\sn{1}{6} was computed at each Newton step using method 2 from
Shadid's work. In this forcing term method, nonlinear residuals from
the two previous Newton steps are used to inform the choice of the
forcing term for the next step. At a Rayleigh number of \sn{1}{6}, a
constant forcing term of \sn{1}{-4} was use to give better convergence
properties.

@@

For the verification calculations, at each Rayleigh number the global
minimum, maximum, and average values were recorded for fluid velocity
in the x and y directions, fluid pressure, and fluid
temperature. Tables~\ref{tab:convection_ra1e3_results},
\ref{tab:convection_ra1e4_results},
\ref{tab:convection_ra1e5_results}, and
\ref{tab:convection_ra1e6_results} give the results of these
computations. It should be noted that the negative pressures computed
are due to a relative pressure being reported. For each of the data
points presented, both Newton-Krylov solutions and FANM solutions
computed identical numerical results for all of these global
values. No variation in solution was noted for each of the
computations larger than the tolerance of the converged nonlinear
residual norms given in
Table~\ref{tab:convection_residual_norm_comparison}. Variations in the
convergence behavior and differences in performance for these
solutions will be analyzed in the following section.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ccc}\hline\hline
      \multicolumn{1}{c}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      \sn{1}{3} & \sn{4.542}{-14} & \sn{1.208}{-14} \\
      \sn{1}{4} & \sn{1.045}{-12} & \sn{7.012}{-13} \\
      \sn{1}{5} & \sn{1.784}{-12} & \sn{1.059}{-12} \\
      \sn{1}{6} & \sn{3.404}{-12} & \sn{3.479}{-12} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:convection_residual_norm_comparison}
\end{table}

@@

A Drekar model of thermal convection cavity problem was solved using
both the Newton-Krylov solver and the FANM solver for Reynolds numbers
of 100, 300, 500, and 700 on a $50 \times 50$ square
grid. Table~\ref{tab:lid_driven_parameters} gives the physical
parameters of the problem and Table~\ref{tab:driven_mcsa_parameters}
gives the MCSA solver parameters used within the FANM
method. Variation in the Reynolds number of the system was achieved by
keeping the parameters given in Table~\ref{tab:lid_driven_parameters}
fixed and varying the fluid velocity in the $x$ direction on the top
boundary. In addition to multigrid preconditioning for the linear
solution at each Newton step, a polynomial line search method was used
as a means of globalization assisting the Newton correction
computation as outlined by Pawlowski in
\citep{pawlowski_globalization_2006} while the forcing term was again
computed using method 2 from Shadid's work \citep{shadid_inexact_1997}
at all Reynolds numbers.

@@

For the verification calculations, at each Reynolds number the global
minimum, maximum, and average values were recorded for the fluid
velocity in the x and y directions and the fluid
pressure. Tables~\ref{tab:driven_re100_results},
\ref{tab:driven_re300_results}, \ref{tab:driven_re500_results}, and
\ref{tab:driven_re700_results} give the results of these
computations. As with the thermal convection problem, the negative
pressures computed are due to a relative pressure being reported. For
each of the data points given, both Newton-Krylov solutions and FANM
solutions computed identical numerical results for all of these global
values. The norm of the converged nonlinear residual for the
calculations is given in
Table~\ref{tab:driven_residual_norm_comparison}. All computed global
values were within these tolerances.

@@

A Drekar model of the backward facing step problem was solved using
both the Newton-Krylov solver and the FANM solver for Reynolds numbers
of 200, 300, 400, and 500 on a $20 \times 250$ rectangular
grid. Table~\ref{tab:backward_step_parameters} gives the physical
parameters of the problem and Table~\ref{tab:step_mcsa_parameters}
gives the MCSA solver parameters used within the FANM
method. Variation in the Reynolds number of the system was achieved by
keeping the parameters given in
Table~\ref{tab:backward_step_parameters} fixed and varying the maximum
fluid velocity in the parabolic inlet condition. In addition to
multigrid preconditioning for the linear solution at each Newton step,
a polynomial line search method was used as a means of globalization
assisting the Newton correction computation as outlined by Pawlowski
in \citep{pawlowski_globalization_2006} while the forcing term was
again computed using method 2 from Shadid's work
\citep{shadid_inexact_1997}.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point Iteration & Richardson \\
      Estimator & Adjoint Collision \\
      Histories, Re=200 & 500,000 per iteration \\
      Histories, Re=300 & 500,000 per iteration \\
      Histories, Re=400 & 500,000 per iteration \\
      Histories, Re=500 & 1,000,000 per iteration \\
      Reduced Domain Fill Level, All Re & 200 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification MCSA solver
      parameters.} \textit{No relaxation parameters or variance
      reduction techniques were used with MCSA other than the reduced
      domain approximation. The same fill level for the reduced domain
      approximation was used at every Reynold numbers and different
      histories per iteration were used at different Reynolds numbers
      due to convergence requirements.}}
  \label{tab:step_mcsa_parameters}
\end{table}

@@

For the verification calculations, at each Reynolds number the global
minimum, maximum, and average values were recorded for the fluid
velocity in the x and y directions and the fluid
pressure. Tables~\ref{tab:step_re200_results},
\ref{tab:step_re300_results}, \ref{tab:step_re400_results}, and
\ref{tab:step_re500_results} give the results of these computations.
The norm of the converged nonlinear residual for the calculations is
given in Table~\ref{tab:step_residual_norm_comparison}. The
Newton-Krylov solutions and FANM solutions computed identical
numerical results for all of these global values within converged
tolerances.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 8.776187720E+01 & 8.776187720E+01 \\
      Minimum $U$ & -2.796828970E+01 & -2.796828970E+01 \\
      Maximum $U$ & 2.639993990E+02 & 2.639993990E+02 \\
      \hline
      Average $V$ & -8.870766180E-01 & -8.870766180E-01 \\
      Minimum $V$ & -2.636357380E+01 & -2.636357380E+01 \\
      Maximum $V$ & 1.330345700E+01 & 1.330345700E+01 \\
      \hline
      Average $P$ & 1.226960220E+04 & 1.226960220E+04 \\ 
      Minimum $P$ & 2.953808400E+01 & 2.953808400E+01 \\ 
      Maximum $P$ & 2.202121190E+04 & 2.202121190E+04 \\ 
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 200.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re200_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 1.316701890E+02 & 1.316701890E+02 \\
      Minimum $U$ & -4.357431070E+01 & -4.357431070E+01 \\
      Maximum $U$ & 3.958553050E+02 & 3.958553050E+02 \\
      \hline
      Average $V$ & -1.330267460E+00 & -1.330267460E+00 \\
      Minimum $V$ & -3.467114630E+01 & -3.467114630E+01 \\
      Maximum $V$ & 1.694243270E+01 & 1.694243270E+01 \\
      \hline
      Average $P$ & 1.681552980E+04 & 1.681552980E+04 \\
      Minimum $P$ & 4.129311640E+01 & 4.129311640E+01 \\
      Maximum $P$ & 2.940820620E+04 & 2.940820620E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 300.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re300_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 1.759720450E+02 & 1.759720450E+02 \\
      Minimum $U$ & -5.941731260E+01 & -5.941731260E+01 \\
      Maximum $U$ & 5.287146290E+02 & 5.287146290E+02 \\
      \hline
      Average $V$ & -1.776706740E+00 & -1.776706740E+00 \\
      Minimum $V$ & -4.497362670E+01 & -4.497362670E+01 \\
      Maximum $V$ & 1.973372840E+01 & 1.973372840E+01 \\
      \hline
      Average $P$ & 1.954352940E+04 & 1.954352940E+04 \\
      Minimum $P$ & 5.294095080E+01 & 5.294095080E+01 \\
      Maximum $P$ & 3.457969480E+04 & 3.457969480E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 400.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re400_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U$ & 2.199858290E+02 & 2.199858290E+02 \\
      Minimum $U$ & -7.549221730E+01 & -7.549221730E+01 \\
      Maximum $U$ & 6.605863330E+02 & 6.605863330E+02 \\
      \hline
      Average $V$ & -2.220108250E+00 & -2.220108250E+00 \\
      Minimum $V$ & -5.888473080E+01 & -5.888473080E+01 \\
      Maximum $V$ & 2.201938360E+01 & 2.201938360E+01 \\
      \hline
      Average $P$ & 1.983947940E+04 & 1.983947940E+04 \\
      Minimum $P$ & -9.707913370E+03 & -9.707913370E+03 \\
      Maximum $P$ & 3.771193860E+04 & 3.771193860E+04 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification for a
      Reynolds number of 500.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re500_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ccc}\hline\hline
      \multicolumn{1}{c}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      200 & 1.939E-11 & 1.975E-11 \\
      300 & 2.786E-11 & 2.751E-11 \\
      400 & 3.360E-11 & 3.597E-11 \\
      500 & 5.824E-11 & 4.062E-11 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:step_residual_norm_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ccc}\hline\hline
      \multicolumn{1}{c}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      \sn{1}{3} & 5 & 5 \\
      \sn{1}{4} & 7 & 7 \\
      \sn{1}{5} & 9 & 10 \\
      \sn{1}{6} & 11 & 11 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:convection_nonlinear_iter_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ccc}\hline\hline
      \multicolumn{1}{c}{Rayleigh Number}& 
      \multicolumn{1}{c}{GMRES Iterations}&
      \multicolumn{1}{c}{MCSA Iterations}\\
      \hline
      \sn{1}{3} & 23 & 18 \\
      \sn{1}{4} & 23 & 17 \\
      \sn{1}{5} & 25 & 20 \\
      \sn{1}{6} & 39 & 25 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity total sum of linear
      iterations for all nonlinear iterations.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:convection_linear_iter_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cc}\hline\hline
      \multicolumn{1}{c}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      \sn{1}{3} & 338 \\
      \sn{1}{4} & 336 \\
      \sn{1}{5} & 346 \\
      \sn{1}{6} & 465 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:convection_speedup_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ccc}\hline\hline
      \multicolumn{1}{c}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      100 & 6 & 6 \\
      300 & 9 & 9 \\
      500 & 11 & 11 \\
      700 & 14 & 10 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:driven_nonlinear_iter_comparison}
\end{table}
